Interpolation and Extrapolation Performance Measurement of Analytical and ANN-Based Flow Laws for Hot Deformation Behavior of Medium Carbon Steel

### 2023-02-10 Article.tex
Update Acknowledgments section

% Author Orchid ID: enter ID or remove command
\newcommand{\orcidauthorA}{0000-0001-7367-5453} % Add \orcidA{} behind the author's name
\newcommand{\orcidauthorB}{0000-0002-1522-2787} % Add \orcidB{} behind the author's name

% Authors, for the paper (add full first names)
\Author{Pierre Tize Mha$^{1}$, Prashant Dhondapure$^{2}$, Mohammad Jahazi$^{2}$\orcidB{}, Amèvi Tongne$^{1}$, Olivier Pantalé *$^{1}$\orcidA{}}

@@

% Affiliations / Addresses (Add [1] after \address if there is only one affiliation.)
\address{
$^{1}$ \quad Laboratoire Génie de Production, INP/ENIT, Université de Toulouse, 47 Av d'Azereix, F-65016 Tarbes, France\\
$^{2}$ \quad École de Technologie Supérieure, 1100 Notre Dame St. W., QC H3C 1K3, Montréal, Canada}

@@

The material used in this study consists of a medium carbon steel whose chemical composition is given in Table \ref{tab:Composition}.
\begin{table}[h!]
\centering
\caption{Chemical composition of medium carbon steel, Fe = balance}
\begin{tabular}{lccccccc}
	\toprule
	\textbf{Element} & \textbf{C} & \textbf{Mn} & \textbf{Mo} & \textbf{Si} & \textbf{Ni} & \textbf{Cr} & \textbf{Cu} \\ \midrule
	\textbf{Wt~\%}   &   $0.30$   &   $0.89$    &   $0.52$    &   $0.34$    &   $0.68$    &   $1.86$    &   $0.17$    \\ \bottomrule
\end{tabular}
\label{tab:Composition}
\end{table}
Cylindrical samples were machined with an initial diameter of $d=10$~mm and a height of $h_0=15$~mm.
Hot compression tests were performed on a Gleeble-3800 thermomechanical simulator (see Figure \ref{fig:Gleeble3800}), for $5$ temperature levels, namely, $1050\celsius$, $1100\celsius$, $1150\celsius$, $1200\celsius$ and $1250\celsius$, with the $6$ strain rates of $0.001~\ps$, $0.01~\ps$, $0.1~\ps$, $1~\ps$, $2.0~\ps$ and $5~\ps$.
\begin{figure}[!ht]
\centering
\includegraphics[width=0.7\columnwidth]{Figures/Gleeble-3800}
\caption{The Gleeble-3800 thermomechanical simulator system used for this study}
\label{fig:Gleeble3800}
\end{figure}
Thin tantalum sheets were used as lubricating material at the contact surface of the anvils and samples to minimize friction during testing.
As shown in Figure \ref{fig:GleebleProcess}, the samples were heated to a temperature of $1260\celsius$ with a heating rate of $2$\celsius/s and held at this temperature for $5$~min to eliminate thermal gradients.
They were then cooled down with a rate of $1$\celsius/s to the test temperature and then held at constant temperature for $1$~min before deformation.
During the compression phase, the temperature of the specimen is kept constant by the thermal control system of the machine.
After compression, the specimen is quickly quenched to freeze its microstructure for later analysis.
Figure \ref{fig:GleebleProcess} also shows the aspects of the specimens before and after the compression test: $h_0$ and $r_0$ are the height and radius before compression and $h$, $r_m$ and $r_t$ are the height, large radius and small radius of the specimen after compression, respectively.
\begin{figure}[!ht]
\centering
\includegraphics[width=0.8\columnwidth]{Figures/GleebleProcess}
\caption{Schematic diagram of the experimental process}
\label{fig:GleebleProcess}
\end{figure}

@@

\begin{table}[h!]
\centering
\caption{Parameter values of the Hansel-Spittel flow law for the medium carbon steel}
\begin{tabular}{ccccc}
	\toprule
	   \boldmath{$A$}    &    \boldmath{$m_1$}    & \boldmath{$m_2$} &   \boldmath{$m_3$}   &   \boldmath{$m_4$}    \\
	$5.954\times 10^{3}$ & $-3.3576\times10^{-3}$ &     $0.2641$     &      $-0.0868$       & $2.2688\times10^{-4}$ \\ \midrule
	                     &    \boldmath{$m_5$}    & \boldmath{$m_6$} &   \boldmath{$m_7$}   &   \boldmath{$m_8$}    \\
	                     & $-4.2163\times10^{-4}$ &    $-0.0561$     & $2.264\times10^{-4}$ &          $0$          \\ \bottomrule
\end{tabular}
\label{tab:HS}
\end{table}

@@

\acknowledgments{The authors acknowledge Finkl Steel-Sorel Co., École de Technologie Supérieure, and École Nationale d’Ingénieurs de Tarbes, France, for providing technical data, materials, and testing facilities.}

>>>>

% Author Orchid ID: enter ID or remove command
\newcommand{\orcidauthorA}{0000-0001-7367-5453} % Add \orcidA{} behind the author's name
\newcommand{\orcidauthorB}{0000-0002-1522-2787} % Add \orcidB{} behind the author's name
\newcommand{\orcidauthorC}{0000-0002-5360-5121}

% Authors, for the paper (add full first names)
\Author{Pierre Tize Mha$^{1}$, Prashant Dhondapure$^{2}$, Mohammad Jahazi$^{2}$\orcidB{}, Amèvi Tongne$^{1}$\orcidC{}, Olivier Pantalé $^{1*}$\orcidA{}}

@@

% Affiliations / Addresses (Add [1] after \address if there is only one affiliation.)
\address{$^{1}$ \quad Laboratoire Génie de Production, INP/ENIT, Université de Toulouse, 47 Av d'Azereix, F-65016 Tarbes, France\\
$^{2}$ \quad École de Technologie Supérieure, 1100 Notre Dame St. W., QC H3C 1K3, Montréal, Canada}

@@

The material used in this study consists of a medium carbon steel whose chemical composition is given in Table \ref{tab:Composition}.
\begin{table}[h!]
\centering
\caption{Chemical composition of medium carbon steel, Fe = balance}
\begin{tabular}{lccccccc}
\toprule
\textbf{Element} & \textbf{C} & \textbf{Mn} & \textbf{Mo} & \textbf{Si} & \textbf{Ni} & \textbf{Cr} & \textbf{Cu} \\ 
\midrule
\textbf{Wt~\%} & $0.30$ & $0.89$ & $0.52$ & $0.34$ & $0.68$ & $1.86$ & $0.17$ \\ 
\bottomrule
\end{tabular}
\label{tab:Composition}
\end{table}
Cylindrical samples were machined with an initial diameter of $d=10$~mm and a height of $h_0=15$~mm.
Hot compression tests were performed on a Gleeble-3800 thermomechanical simulator (see Figure \ref{fig:Gleeble3800}), for $5$ temperature levels, namely, $1050\celsius$, $1100\celsius$, $1150\celsius$, $1200\celsius$ and $1250\celsius$, with the $6$ strain rates of $0.001~\ps$, $0.01~\ps$, $0.1~\ps$, $1~\ps$, $2.0~\ps$ and $5~\ps$.
\begin{figure}[!ht]
\centering
\includegraphics[width=0.7\columnwidth]{Figures/Gleeble-3800}
\caption{The Gleeble-3800 thermomechanical simulator system used for this study}
\label{fig:Gleeble3800}
\end{figure}
Thin tantalum sheets were used as lubricating material at the contact surface of the anvils and samples to minimize friction during testing.
As shown in Figure \ref{fig:GleebleProcess}, the samples were heated to a temperature of $1260\celsius$ with a heating rate of $2$\celsius/s and held at this temperature for $5$~min to eliminate thermal gradients.
They were then cooled down with a rate of $1$\celsius/s to the test temperature and then held at constant temperature for $1$~min before deformation.
During the compression phase, the temperature of the specimen is kept constant by the thermal control system of the machine.
After compression, the specimen is quickly quenched to freeze its microstructure for later analysis.
Figure \ref{fig:GleebleProcess} also shows the aspects of the specimens before and after the compression test: $h_0$ and $r_0$ are the height and radius before compression and $h$, $r_m$ and $r_t$ are the height, large radius and small radius of the specimen after compression, respectively.
\begin{figure}[!ht]
\centering
\includegraphics[width=0.8\columnwidth]{Figures/GleebleProcess}
\caption{Schematic diagram of the experimental process on the Gleeble-3800 thermomechanical simulator}
\label{fig:GleebleProcess}
\end{figure}

@@

\begin{table}[h!]
\centering
\caption{Parameter values of the Hansel-Spittel flow law for the medium carbon steel}
\begin{tabular}{ccccc}
\toprule
\boldmath{$A$} & \boldmath{$m_1$} & \boldmath{$m_2$} & \boldmath{$m_3$} & \boldmath{$m_4$} \\ 
\midrule
$5.954\times 10^{3}$ & $-3.3576\times10^{-3}$ & $0.2641$ & $-0.0868$ & $2.2688\times10^{-4}$ \\ 
\toprule
& \boldmath{$m_5$} & \boldmath{$m_6$} & \boldmath{$m_7$} & \boldmath{$m_8$} \\ 
\midrule
& $-4.2163\times10^{-4}$ & $-0.0561$ & $2.264\times10^{-4}$ & $0$ \\ 
\bottomrule
\end{tabular}
\label{tab:HS}
\end{table}

@@

\acknowledgments{The authors acknowledge Mr. Jean-Benoit Morin, Director of Metallurgy and Quality from Finkl Steel-Sorel, Dr. Abdelhalim Loucif from R\&D department of Finkl Steel-Sorel, Ecole de Technologie Superieure, and Ecole Nationale d’Ingenieurs de Tarbes, France, for providing technical data, materials, and testing facilities.}
